# Reproducible Research: Peer Assessment 1

This is the first peer assessment in Reproducible Research Coursera Course.

In this assessment will be tried to make a report answer some questions.

## Loading and preprocessing the data

First of all it will be load the data file in a data frame.

```{r}
data<-read.csv('activity.csv')
summary(data)
```


## What is mean total number of steps taken per day?

In the first question, it will be made a histogram and reported the mean and median total number of step per day.

Let's calculate the total steps per day and create a new data frame.

```{r}
steps_day <- tapply(data$steps, data$date, sum, na.rm=TRUE)

```

Histogram of total steps per day. 

```{r}
hist(steps_day, main="Histogram of total Steps per day", xlab="Steps")
```

It will be calculated the mean and the median and reported.

```{r}
steps_mean <- mean(steps_day)
steps_median <- median(steps_day)
```

Mean: `r steps_mean`

Median: `r steps_median`

## What is the average daily activity pattern?

Calculate the average daily each interval and plot.

```{r}
steps_interval <- tapply(data$steps, data$interval, mean, na.rm=TRUE)
#plot
plot(names(steps_interval), steps_interval, main="Daily Average", xlab="Intervals", col="red", type="l", ylab="Steps")
```

It will be calculated and reported the interval with max average:

```{r}
steps_interval[which.max(steps_interval)]
```

## Imputing missing values

Count the NA in dataset.

```{r}
length(data$steps[is.na(data$steps)])
# or: length(subset(data$steps, is.na(data$steps)))
```

Now it will be created a new dataset and used the above mean *steps_interval* of each interval for the NA values.And present the plot

```{r}
newdata <- data
newdata$steps[is.na(newdata$steps)] <- mean(steps_interval)
newsteps_day <- tapply(newdata$steps, newdata$date, sum, na.rm=TRUE)
```

New histogram, mean and media:

```{r}
hist(newsteps_day)
newsteps_mean <- mean(newsteps_day)
newsteps_median <- median(newsteps_day)
```

Mean: `r newsteps_mean`

Median: `r newsteps_median`

## Are there differences in activity patterns between weekdays and weekends?

It will be caculated weekday for all days, calculated the interval mean by weekdays and weekends and ploted separated.

```{r}
# Locale to English needed for week names.
Sys.setlocale(category = "LC_ALL", locale = "C")
newdata$rdate <- strptime(newdata$date,"%Y-%m-%d")
newdata$wde <- weekdays(newdata$rdate,  abbreviate=TRUE) %in% c("Sat", "Sun")
newdata_wend <- newdata[newdata$wde,]
newdata_wday <- newdata[newdata$wde==FALSE,]

steps_wend <- tapply(newdata_wend$steps, newdata_wend$interval, mean, na.rm=TRUE)
steps_wday <- tapply(newdata_wday$steps, newdata_wday$interval, mean, na.rm=TRUE)
par(mcol=c(2,1))
plot(names(steps_wend), steps_wend, main="Steps Weekend", xlab="Intervals", col="red",
     type="l", ylab="Steps")
plot(names(steps_wday), steps_wday,  main="Steps Weekday", xlab="Intervals", col="blue",
     type="l", ylab="Steps")
```
